Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-02-23 scripts/04_downstream_analysis.Rmd
ENH GO term enrichment analysis now works

```{r go_term_enrichment}

```

>>>>

```{r go_to_gene_mapping}

genes = getBM(attributes=c("go_id", "refseq_mrna"), values=gene_names, filters="refseq_mrna",
	      mart=ensembl)

# Create gene to GO id mapping
gene_id_go_mapping = NULL
i = 1
for(gene in gene_names){
    go_terms = genes[genes[, "refseq_mrna"] == gene, "go_id"]
    if(length(go_terms) != 0){
        gene_id_go_mapping$gene = go_terms
	names(gene_id_go_mapping)[i] = gene
	i = i + 1
    }
}
```

```{r go_term_enrichment, results="hide"}
source("GO_terms_analysis.R")

all_go_terms = data.frame()
for(cluster in clusters){

    scores = as.numeric(labels == cluster)
    names(scores) = gene_names
    go_terms_enriched = find_enriched_go_terms(
	scores,
    	gene_id_go_mapping)

    if((dim(all_go_terms)[1] == 0) & (dim(go_terms_enriched)[1] != 0)){
	go_terms_enriched["Cluster"] = cluster
	all_go_terms = go_terms_enriched
    }else if(dim(go_terms_enriched)[1] != 0){
	go_terms_enriched["Cluster"] = cluster
	all_go_terms = merge(all_go_terms, go_terms_enriched, all=TRUE)
    }

}
```

all_go_terms = all_go_terms[
    order(all_go_terms["Cluster",],
	  all_go_terms["resultFisher.p.adj",])]

kable(all_go_terms, "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```
